Understanding the Impact of Mortgage State and Income on Household Poverty Status

### 2024-04-18 paper/US_Poverty_Analysis_2019.qmd
final checks

\newpage
# Introduction
Despite many policies the United States have implemented to mitigate poverty, there has been no real improvement [@Kearney_Harris]. Poverty remains a major issue in the US, affecting millions of people. In 2019, the poverty rate was 10.5%, which was approximately 34.0 million people [@Semega_2022]. Therefore, we want to find out the causes of poverty, in order to reduce it. Multiple research, using the Official Poverty Measure dataset gathered by the United States Census Bureau (USCB), looked at why poverty persists. USCB is an agency of the U.S. Federal Statistical System, responsible for producing data about the American people and economy  [@uscb]. Over the years, people have realized that the Official Poverty Measure is flawed in various aspects, such as not accounting for regional differences in costs of living, not considering household's mortgage state, and government benefits programs  [@Gesumaria_2015]. Therefore, Supplemental Poverty Measure was developed to address numerous concerns of Official Poverty Measure critics, providing an improved statistical picture of poverty. In this paper, we will analyze why some US household are in poverty in 2019 using the 2019 Revised Supplemental Poverty Measure (SPM) Research dataset from the United States Census Bureau (USCB) [@Bureau_2022]. We build a prediction model for households poverty status using 2019 Revised SPM dataset. This allows us to look at the question whether potential financial factors may influence the poverty status for US households in 2019.

>>>>

\newpage
# Introduction
Despite many policies the United States have implemented to mitigate poverty, there has been no real improvement [@Kearney_Harris]. Poverty remains a major issue in the US, affecting millions of people. In 2019, the poverty rate was 10.5%, which was approximately 34.0 million people [@Semega_2022]. Therefore, we want to find out the causes of poverty, in order to reduce it. Multiple research, using the Official Poverty Measure dataset gathered by the United States Census Bureau (USCB), looked at why poverty persists. USCB is an agency of the U.S. Federal Statistical System, responsible for producing data about the American people and economy [@uscb]. Over the years, people have realized that the Official Poverty Measure is flawed in various aspects [@Gesumaria_2015]. Therefore, Supplemental Poverty Measure was developed to address numerous concerns of Official Poverty Measure critics, providing an improved statistical picture of poverty. In this paper, we will analyze why some US household are in poverty in 2019 using the 2019 Revised Supplemental Poverty Measure (SPM) Research dataset from the United States Census Bureau (USCB) [@Bureau_2022]. We build a prediction model for households poverty status using 2019 Revised SPM dataset. This allows us to look at the question whether potential financial factors may influence the poverty status for US households in 2019.
